---
title: "Reproducible Research - Peer Assessment 1"
author: "Tim Parkins"
date: '2017-03-06'
output: html_document
---

```{r setup, include=FALSE}

      knitr::opts_chunk$set(echo = TRUE)

```

## Introduction  

This assignment makes use of data from a personal activity monitoring device. This device collects data at 5 minute intervals through out the day. The data consists of two months of data from an anonymous individual collected during the months of October and November, 2012 and include the number of steps taken in 5 minute intervals each day.

## Data  

The data for this assignment can be downloaded from the course web site:

 - *Dataset:* [Activity monitoring data](https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip) [52K]  


The variables included in this dataset are:

- steps: Number of steps taking in a 5-minute interval (missing values are coded as NA)

- date: The date on which the measurement was taken in YYYY-MM-DD format

- interval: Identifier for the 5-minute interval in which measurement was taken

The dataset is stored in a comma-separated-value (CSV) file and there are a total of 17,568 observations in this dataset.

```{r load_data}
      # load the data
      activity <- read.csv("activity.csv", header=TRUE)
      activity$date <- as.Date(activity$date, format="%Y-%m-%d")
      
```

## Loading and preprocessing the data



## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
